Evolution of solar wind discontinuities in the inner heliosphere

### 2024-08-26 article.qmd
update: figures

<!-- ![](figures/density_distribution.png) -->

@@

![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current.spc_n_spc.png){#fig-comp-map}

![](figures/enc2/density_distribution.spi_n_spi.png)

Solar wind properties

L:
j:
$\Delta v_l$

![](figures/enc2/thickness_current.spi_n_spi.png)

Scale-dependent properties of current sheets in the solar wind

>>>>

TODO: how does the results depend on the period selected for the conjunctions and alignments?

@@

![](figures/enc7/properties_distribution.svg)

Thickness and current density relationship
Scale-dependent properties of current sheets in the solar wind

![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
